\sysfull

### 2018-04-15 paper/newCoalescing.tex
correct algo 1

When incoming energy is sufficient to run multiple consecutive tasks,
committing state after each task is wasteful. \sys mitigates this
waste by deferring the expensive commits and performing them in a
batch. In the resulting execution, several tasks are \emph{merged} into a
single virtual task---a process we call \emph{coalescing}. 
%
When $N$ tasks are coalesced, $N-1$ boundaries are crossed and some number of
pages are dirtied. The first $N-2$ executions of \transition statement skip
committing dirty pages to non-volatile memory, leaving the work of committing
pages modified by any of the $N$ tasks to the statement $N-1$.
Coalescing reduces the total number of non-volatile memory
accesses, because when coalesced tasks access the same pages of data, only the
last version of the page needs to be committed.  
\textcolor{red}{maybe is possible to demonstrate with data? count number of executed non-volatile vs volatile accesses}

\textbf{Trade-off between Speed and Wasted Effort.} \sys can coalesce an
arbitrary number of consecutive tasks. However, as more tasks coalesce, their
collective commit overhead amortizes better, but the risk of wasting work also
increases. If power fails during a long sequence of coalesced tasks, execution
will restart from the last commit, i.e. the first task in the sequence, losing
the progress made by any of the coalesced tasks.  The challenge to coalescing
tasks is determining how many tasks to coalesce before committing.
%
%During execution, an executing task is either a {\em coalesced} task, which
%does not commit its state before transitioning or a {\em committing} task,
%which does commit its state before transitioning.

@@

        \While{$\texttt{true}$}
	        \State $ B_\text{c} \gets B$
	        \While{$ B_\text{c} > 0$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        % \State $W$ \gets \Call{f_\text{weight}}{$T_\texttt{i}$}
		        \State $B_\text{c} \gets B_\text{c} - W$
				\State $H_\text{c} \gets H_\text{c} + W$
	        \EndWhile
	        % \State $B$ \gets \Call{f\_compl}{$\texttt{B},\texttt{H_\text{c}},\texttt{H_\text{p}}$}
	        \State \Call{commit\_to\_fram}{}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
%
%
The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime.

To describe the proposed strategies we will use the following parameters: \\
(i) \textit{target budget B}: total number of static tasks to be coalesced; (ii) \textit{current budget $B_\text{c}$}: remaining number of tasks to be coalesced before committing to non-volatile memory; (iii) \textit{history H}: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.

>>>>

When incoming energy is sufficient to run multiple consecutive tasks,
committing state after each task is wasteful. \sys mitigates this
waste by deferring the expensive commits and performing them in a
batch. In the resulting execution, several tasks are \emph{merged} into a
single virtual task---a process we call \emph{coalescing}. 
%
When $N$ tasks are coalesced, $N-1$ boundaries are crossed and some number of
pages are dirtied. The first $N-2$ executions of \transition statement skip
committing dirty pages to non-volatile memory, leaving the work of committing
pages modified by any of the $N$ tasks to the statement $N-1$.
Coalescing reduces the total number of non-volatile memory
accesses, because when coalesced tasks access the same pages of data, only the
last version of the page needs to be committed.  
\textcolor{red}{maybe is possible to demonstrate with data? count number of executed non-volatile vs volatile accesses}
%
\textbf{Trade-off between Speed and Wasted Effort.} \sys can coalesce an
arbitrary number of consecutive tasks. However, as more tasks coalesce, their
collective commit overhead amortizes better, but the risk of wasting work also
increases. If power fails during a long sequence of coalesced tasks, execution
will restart from the last commit, i.e. the first task in the sequence, losing
the progress made by any of the coalesced tasks.  The challenge to coalescing
tasks is determining how many tasks to coalesce before committing.
%
%During execution, an executing task is either a {\em coalesced} task, which
%does not commit its state before transitioning or a {\em committing} task,
%which does commit its state before transitioning.

@@

        \While{$\texttt{true}$}
	        \State $ B_\text{c} \gets B$
	        \While{$ B_\text{c} > 0$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        % \State $W$ \gets \Call{f_\text{weight}}{$T_\texttt{i}$}
		        \State $B_\text{c} \gets B_\text{c} - W$
				\State $H_\text{c} \gets H_\text{c} + W$
	        \EndWhile
	        % \State $B$ \gets \Call{f\_compl}{$\texttt{B},\texttt{H_\text{c}},\texttt{H_\text{p}}$}
	         \State $B \leftarrow $ \Call{$f_\text{reboot}$}{B, $H_\text{c}$,$H_\text{p}$}
	        \State \Call{commit\_to\_fram}{}
        \EndWhile
	\end{algorithmic}
\end{algorithm}
%
%
The likelihood that a task group will complete depends on the total amount of
energy consumed by all tasks in the group, i.e. the size of the dynamic task.
%
A good coalescing strategy must moderate the risk of wasted work and capitalize
on benefits of deferred commits by adapting the target size of the dynamic task
to the energy available at runtime. 
%
To describe the proposed strategies we will use the following parameters:
\begin{itemize}
\item target budget $B$: total number of static tasks to be coalesced.
\item current budget $B_\text{c}$: remaining number of tasks to be coalesced before committing to non-volatile memory; 
\item history $H$: up on reboot, it is the number of executed static tasks between the last two power interrupts. While executing, it is the number of executed static tasks since the last power interrupt.
\end{itemize}
